Project report

### 2018-02-14 ProjectReport/BigDataHomework.tex
Update report, add images, etc

	\tableofcontents
    \newpage
	\listoffigures
	\newpage
	\listoftodos
	\newpage

@@

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.75] {questionCexample.jpg}
			\caption{Example of a trip visualization.}
		\end{center}
    \label{gmlplot_example}
	\end{figure}

@@

  To visualize the neighbours, the \texttt{visualize\_nns}
  function is used, where three lists are created:
  \begin{enumerate}
    \item a list with all the route points (longitudes and latitudes) of the
      test trip and its neighbours
    \item a list with the journey labels and the nn computation data
      \item a list with the colors with which to draw (all blue in this
        question).
      \end{enumerate}
      All this data is provided to the
      \texttt{utils.visualize\_point\_sequences} function. This function is
      supplied with point sequences with corresponding color sequences, and
      produces colored gml plot maps with the \texttt{write\_group\_gml}
      function. Each html output map is converted to a png image using a conversion tool in the \texttt{html\_to\_png} function, in
order to automate image creation from the generated maps (the tool is the
\texttt{rasterize.js} utility from the \texttt{phantomjs} module).
However we found the gml plot zoom difficult to automatically configure correctly so that
all points are visible, and thus the images in the report were fetched with a printscreen.
The converted images are used to create 6 subplots (1 test trip + k=5 nearest
neighbours). All plotting is done with the pylab package.
l 
	An example of this question image output can be found below:

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {question2a1example.jpg}
			\caption{Example of nearest neighbours trips visualization}
		\end{center}
	\end{figure}

@@

	Below there is an example of the 6 produced maps, showing the nearest sub-routes related to a test trip:

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.50] {question2a2example.jpg}
			\caption{Example of nearest sub-routes trips visualization}
		\end{center}
	\end{figure}

@@

  \begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
      method & train & val \\ \hline
      logreg & 0.123 & 0.0123 \\ \hline

      % ...
\hline
      improvements & & \\ \hline
       impr.method1 & 123123 & 3412312 \\ \hline
    \end{tabular}
    \end{table}
	\subsection{Test improved classifier}
  We tested the improved classifier in the test data. The results are attached
  in the specified format to the file \texttt{testSet\_journeyPatternIDs.csv}.

>>>>

	\tableofcontents
    \newpage
	\listoffigures
	\newpage

@@

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.55] {questionC1.png}
			\caption{First trip visualization.}
		\end{center}
    \label{gmlplot_example}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.60] {questionC2.png}
			\caption{Second trip visualization.}
		\end{center}
		\label{gmlplot_example}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.75] {questionC3.png}
			\caption{Third trip visualization.}
		\end{center}
		\label{gmlplot_example}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.75] {questionC4.png}
			\caption{Third trip visualization.}
		\end{center}
		\label{gmlplot_example}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.75] {questionC5.png}
			\caption{Third trip visualization.}
		\end{center}
		\label{gmlplot_example}
	\end{figure}

@@

  To visualize the neighbours, the \texttt{visualize\_nns}
  function is used, where three lists are created:
  \begin{enumerate}
    \item a list with all the route points (longitudes and latitudes) of the
      test trip and its neighbours
    \item a list with the journey labels and the nn computation data
      \item a list with the colors with which to draw (all blue in this
        question).
      \end{enumerate}
      All this data is provided to the
      \texttt{utils.visualize\_point\_sequences} function. This function is
      supplied with point sequences with corresponding color sequences, and
      produces colored gml plot maps with the \texttt{write\_group\_gml}
      function. Each html output map is converted to a png image using a conversion tool in the \texttt{html\_to\_png} function, in
order to automate image creation from the generated maps (the tool is the
\texttt{rasterize.js} utility from the \texttt{phantomjs} module).
However we found the gml plot zoom difficult to automatically configure correctly so that
all points are visible, and thus the images in the report were fetched with a printscreen.
The converted images are used to create 6 subplots (1 test trip + k=5 nearest
neighbours). All plotting is done with the pylab package.

	Below we present the results from this question in the requested format:

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {nn1.jpg}
			\caption{Nearest neighbours for the first test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {nn2.jpg}
			\caption{Nearest neighbours for the second test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {nn3.jpg}
			\caption{Nearest neighbours for the third test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {nn4.jpg}
			\caption{Nearest neighbours for the fourth test trip}
		\end{center}
	\end{figure}

	In \ref{nnresults}, we show the total results for the Nearest Neighbors.

	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{}  & \textbf{Time} & \textbf{id1} & \textbf{d1} & \textbf{id2} & \textbf{d2} & \textbf{id3} & \textbf{d3} & \textbf{id4} & \textbf{d4} & \textbf{id5} & \textbf{d5} \\ \hline
			\textbf{1} & 02:129:716    & 309          & 5.2           & 1599         & 6.6           & 1575         & 6.7           & 608          & 6.9           & 1477         & 8.2           \\ \hline
			\textbf{2} & 01:66:739     & 929          & 4.1           & 955          & 65.5          & 582          & 85.3          & 2291         & 105.6         & 1970         & 106.7         \\ \hline
			\textbf{3} & 02:127:758    & 2060         & 4.8           & 567          & 5.8           & 901          & 6.0           & 554          & 7.8           & 571          & 16.0          \\ \hline
			\textbf{4} & 01:83:246     & 2415         & 2.5           & 603          & 3.5           & 2407         & 3.5           & 786          & 64.4          & 753          & 65.7          \\ \hline
			\textbf{5} & 01:80:492     & 740          & 6.6           & 1304         & 32.4          & 2686         & 46.1          & 3138         & 72.3          & 1435         & 145.1         \\ \hline
		\end{tabular}
	\caption{Nearest Neighbors results}
	\label{nnresults}
	\end{table}

@@

  Below, we present the nearest subroutes for each given test trip:

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {subroutes1.jpg}
			\caption{Nearest subroutes for the first test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {subroutes2.jpg}
			\caption{Nearest subroutes for the second test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {subroutes3.jpg}
			\caption{Nearest subroutes for the third test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {subroutes4.jpg}
			\caption{Nearest subroutes for the fourth test trip}
		\end{center}
	\end{figure}

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.40] {subroutes5.jpg}
			\caption{Nearest subroutes for the fifth test trip}
		\end{center}
	\end{figure}

	As in the Nearest Neighbours case, we have also included the html files in the gmplot folder. in \ref{subres} we show the total results for Nearest Subroutes.

	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{}  & \textbf{Time} & \textbf{id1} & \textbf{pts1} & \textbf{id2} & \textbf{pts2} & \textbf{id3} & \textbf{pts3} & \textbf{id4} & \textbf{pts4} & \textbf{id5} & \textbf{pts5} \\ \hline
			\textbf{1} & 01:62:303     & 491          & 31            & 667          & 31            & 1366         & 22            & 503          & 21            & 426          & 19            \\ \hline
			\textbf{2} & 01:63:755     & 2620         & 42            & 510          & 37            & 1093         & 34            & 426          & 31            & 363          & 30            \\ \hline
			\textbf{3} & 00:32:319     & 200          & 40            & 1885         & 40            & 2763         & 40            & 142          & 39            & 135          & 35            \\ \hline
			\textbf{4} & 00:46:297     & 566          & 32            & 1269         & 21            & 227          & 20            & 2561         & 17            & 252          & 15            \\ \hline
			\textbf{5} & 00:57:303     & 940          & 33            & 1932         & 22            & 1384         & 21            & 1606         & 21            & 1822         & 20            \\ \hline
		\end{tabular}
	\caption{Nearest subroutes results}
	\label{subres}
	\end{table}

@@

 \begin{table}[H]
 	\centering
 	\begin{tabular}{|c|c|c|}
 		\hline
 		\textbf{Strategy}            & \textbf{Train Accuracy} & \textbf{Validation Accuracy} \\ \hline
 		\textbf{KNN}                 & 0.446                   & 0.221                        \\ \hline
 		\textbf{Logistic Regression} & 0.269                   & 0.170                        \\ \hline
 		\textbf{Random Forest}       & 0.969                   & 0.281                        \\ \hline
 	\end{tabular}
 \caption{Classification using KNN, logreg and random forest}
 \label{class}
 \end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		strategy & validaton accuracy & change  \\ \hline
		norm\_l2 &  0.063  &  -62.84\%  \\ \hline
		norm\_l1 &  0.048  &  -71.56\%  \\ \hline
		norm\_max &  0.072  &  -57.34\%  \\ \hline
		scaling &  0.131  &  -22.94\%  \\ \hline
		C\_0.200 &  0.15  &  -11.93\%  \\ \hline
		C\_0.500 &  0.157  &  -7.80\%  \\ \hline
		C\_1.500 &  0.175  &  2.75\%  \\ \hline
		C\_2.000 &  0.178  &  5.05\%  \\ \hline
		vlad &  0.003  &  -97.71\%  \\ \hline

	\end{tabular}
	\label{impr}
	\caption{Classification improvements using logistic regression}
\end{table}

	\subsection{Test improved classifier}

  We tested the improved classifier in the test data. The results are attached
  in the specified format to the file \texttt{testSet\_journeyPatternIDs.csv}.
